---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pkgtemp

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![R-CMD-check](https://github.com/Lightbridge-KS/pkgtemp/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Lightbridge-KS/pkgtemp/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

> R Markdown Template for Developing R Package :package:

## Goal

`pkgtemp` contains as series of [usethis](https://usethis.r-lib.org/index.html) and other commands in an **R Markdown** that provides a template to *kick-start* your R package development process. If you want to use **your own template** from GitHub, this package will facilitate that too.

## Prerequisites

You should be somewhat familiar with how to create R Package. Checkout these resources to learn more:

-   [**R Packages Book**](https://r-pkgs.org/index.html) by Hadley Wickham and Jenny Bryan.

-   [**usethis**](https://usethis.r-lib.org/index.html): a workflow package that `pkgtemp` relies on.

(`pkgtemp` assumes that R package is develop in RStudio. If you use other IDE you may need to adapt your workflow accordingly.)

## Installation

You can install the development version of pkgtemp like so:

``` r
# install.packages("remotes")
remotes::install_github("Lightbridge-KS/pkgtemp")
```

## Templates

-   [**Build Package Template:**](./inst/rmarkdown/templates/build/skeleton/skeleton.Rmd) contains a set of R functions to run in each step of package development.

## Workflow

**Create R Package by:**

``` r
usethis::create_package("~/path/to/yourpkg")
```

**Create R Markdown Template for package development by:**

``` r
pkgtemp::use_pkgbuild_rmd()
```

This will:

-   Create folder `dev/`.

-   Write and open R Markdown file `dev/build.Rmd` (generate locally)

**Go to [build.Rmd](./inst/rmarkdown/templates/build/skeleton/skeleton.Rmd)**. You will see 2 types of command in there:

-   **Non-commented commands:** are the command for initial setup. I recommend you run at the first visit. They are at the top of R Markdown.

-   **Commented commands:** you can choose to run in any order as you like.

### Example

```{r, include = FALSE}
# Reset possible options
options(usethis.description = list())
```

```{r showcase}
# Create a new package -------------------------------------------------
path <- file.path(tempdir(), "yourpkg")
usethis::create_package(path)

# only needed since this session isn't interactive
usethis::proj_activate(path)
.old_wd <- setwd(path) # Only in this example

# Create Rmd Template for PKG Development
pkgtemp::use_pkgbuild_rmd(open = FALSE)
```

## Custom Template

Everyone can have a different package development workflow. This second approach will allows you to use your default template from a file in GitHub.

Here how it works:

-   Create your own R Markdown template for building package in Github. (for example, mine is [here](https://github.com/Lightbridge-KS/workflows-rmd/blob/main/pkgbuild.Rmd))

-   Provide a default GitHub URL where `pkgtemp` will find as your remote template. You'll need to config global option in `~/.Rprofile` as follows.


```{r eval=FALSE}
# To edit `~/.Rprofile`
usethis::edit_r_profile()
```

Copy code below to `~/.Rprofile` and provide your `pkgbuild_url` as URL to your default template.

```{r eval=FALSE}
if (interactive() && requireNamespace("pkgtemp", quietly = TRUE)) {

  pkgtemp::set_github_template_url(
    pkgbuild_url = "https://github.com/OWNER/REPO/blob/REF/path/to/default-template.Rmd"
  )
}
```

-   To use your **default template** from GitHub, create R package as usual and call the previous function `use_pkgbuild_rmd()` with `remote = TRUE`.

```{r eval=FALSE}
pkgtemp::use_pkgbuild_rmd(remote = TRUE)
```

Alternatively, If you want to use any other GitHub template **just once in a while**, provides a `url` directly.

```{r eval=FALSE}
pkgtemp::use_pkgbuild_rmd(url = "https://github.com/OWNER/REPO/blob/REF/path/to/one-off-template.Rmd")
```


------------------------------------------------------------------------

Last updated: `r Sys.Date()`
